\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2016-04-07 paper/paper.tex
references and stuff
stuk van huub + small fixes

@@

\subsection{Fast}
With fast color refinement the colors that lead to refinements are tracked.(TODO: make better explanation) These colors are maintained in a queue. If a color class is being refined, the class is split into two different classes, with one class keeping the old color. The algorithm terminates with a stable coloring if no color class needs refinement, in other words the queue is empty. 
%% TODO %%

>>>>

The fast color refinement algorithm used for this paper is made by W. van Veelen, N. Goldsmid, E. Khan, and E. Koster \cite{misc:group4}, because the original implementation had some issues.

@@

\subsection{Fast}
With fast color refinement the colors that lead to refinements are tracked. These colors are maintained in a queue. If a color class is being refined, the class is split into two different classes, with one class keeping the old color. The algorithm terminates with a stable coloring if no color class needs refinement, in other words the queue is empty.

Fast color refinement is also analyzed. $N$ is again defined as $N=|V(G)|$. Determined is the number of times a vertex $v$ is refined in its worst-case. The color class of $v$ splits at least in half if it is getting refined. The split class with the most vertices in it keeps the original color. If vertex $v$ stays in this original class, $v$ is not refined by definition. It follows that if $v$ gets refined, the degree of the previous color class is at most two times the degree of its new class. Let $k$ be the times $v$ refines in the algorithm, then $2^k$ is the degree of $v$'s original color class.  The degree of the color class is worst-case $N$ if all vertices have the same amount of edges, so worst-case $k=log_2 N$. As shown by P. Bonsma in one of his lectures. \cite{presentation:slidesPartIII}

With the number of edges in a graph times the number of vertices in that graph, the time complexity can be defined.\cite{presentation:slidesPartIII} The time complexity of fast color refinement is $O(m\cdot log n)$.
